Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-06-22 Response/Response 2/response-1.tex

Comments:
The response to the reviewer's concerns are generally satisfying, except the convergence proof.

\vspace{0.1in}
\review{We thank the reviewer for providing valuable and insightful comments.}

For the resubmitted manuscript, the reviewer still has the following concerns

\begin{enumerate}
\cmnt{1} Considering the length of the manuscript, it would be better to shorten some parts that are not new in this manuscript, e.g. III.A. More space can be left for convergence proof, which is very important.

\resp \review{We thank the reviewer for the comment. 
		}

\cmnt{2} In convergence proof (48), why does the 2nd inequality hold? In fact, to prove the feasibility of  \eqn{{m_{k+1}^{(i)}, w_{*}^{(i-1)};m_k^{(i)} }}, the part between 2nd and 3rd inequality is not necessary, ''<=0'' directly follows the 2nd inequality since the solution \eqn{m_{k+1}^{(i)}, \gamma_{k+1}^{(i)} } is the optimal solution, and therefore  feasible.

\resp \review{
	}

\cmnt{3} The solutions SCA iterations \eqn{m^{(i)}_k} does not necessarily converge. In fact \eqn{m} has compact feasible region, and thus \eqn{m^{(i)}_k} has limit points for any specific \eqn{i}.  However \eqn{m_{*}^{(i)}} does not necessarily exist( the whole sequence \eqn{m^{(i)}_k} may be not convergent). Similar problem happens to \eqn{w^{(i)}_k}.

\resp \review {	
}

\cmnt{4} Strict monotonicity with respect to the objective function \eqn{f} should be rigorously proved. Note that to guarantee the uniqueness of the beamformer iterates, (52) instead of the objective function is used.

\resp \review{}

\cmnt{5} Note that the conclusions [32, Thm 2] and [26, Thm 10] have lots of assumptions. To invoke these reference, explicit exposition should be provided to show that these conclusions can be applied to our problem. The same questions occur to the proof in Appendix B, where conclusions in [11] [36] and [37] are used. Too many details are omitted to make the proof convincing and clear.

\resp \review{}

\end{enumerate}

### 2015-06-22 Response/Response 2/response-2.tex

The authors have addressed many of my previous comments. However, there are still several major issues that need further clarification.

\vspace{0.1in}
\review{We would like to thank the reviewer for providing valuable comments.}

\begin{enumerate}
\cmnt{1} The revised paper did not address my previous comment about how to select the sub-channel ordering. I understand that finding the best sub-channel ordering requires exhaustive search which has extremely high complexity. But it is important to provide a guidance on what would be a good choice of sub-channel ordering. For example, can we achieve a good performance by using a low complexity ordering algorithm such as a greedy sub-channel ordering algorithm?

\resp \review{}

\cmnt{2} The authors mentioned that the signaling overhead of the distributed algorithm can be reduced by using a smaller number of iterations \eqn{J_{\max}}. But still, you didn't answer my question about whether the signaling overhead of the distributed algorithm is smaller than the centralized algorithm. You should first analyze the signaling overhead of the distributed algorithm for fixed \eqn{J_{\max}} and the signaling overhead of the centralized algorithm. Then you should point out under what \eqn{J_{\max}} the distributed algorithm will have less signaling overhead than the centralized algorithm. Is it possible that the distributed algorithm always has more signaling overhead than the centralized algorithm even when \eqn{J_{\max} = 1}? Finally, there is a tradeoff between performance and signaling overhead (\eqn{J_{\max}}) for the distributed algorithm. For the same signaling overhead (we can control \eqn{J_{\max}} to make the signaling overhead of the distributed algorithm approximately equal to that of the centralized algorithm), does the distributed algorithm achieve better performance than the centralized algorithm?

\resp \review{
}

\cmnt{3} If the authors can't prove the convergence of the ADMM algorithm (or the decomposition approach via KKT conditions) in Section IV.B, then at least, you should discuss the property of the fixed point of the algorithm. For example, does there exist a fixed point of the algorithm? If so, is the fixed point of the algorithm unique? Is any fixed point of the algorithm also the optimal solution of the original problem in (20)? Assuming that the ADMM algorithm converges to a fixed point, will the interference vector in (39) converges to the actual interference in the network? These questions must be clarified in the paper. Otherwise, it is not clear how the ADMM algorithm is related to the original problem in (20). Similar questions should also be answered for the decomposition approach via KKT conditions.

\resp \review{}

\end{enumerate}

### 2015-06-22 Response/Response 2/response-3.tex

The authors have introduced changes in the manuscript that improved the paper's quality. Additionally, the authors have taken into account the reviewers' comments giving clarifications and modifying the content when required. More specifically, the following aspects have been treated:

\vspace{0.1in}
\review{We thank the reviewer for reading the manuscript and providing valuable comments. The comments are really helps to improve the manuscript.}

\begin{enumerate}
\cmnt{1} Convexity of problem (16). The paragraphs surrounding (16) allow a better understanding of the usage of the additional variables, i.e. gamma and beta, to remove the equality constraint in (2). For the reviewer remains however unclear, the procedure/criterion to determine the operating point for the parameter \eqn{\tilde{\beta}} required in (19) and used in the convex subproblems (20) and (21).

\resp \review{
	}

\cmnt{2} Proof of convergence. The proof of convergence introduced by the authors in the Appendix seems correct and enhances the content of the manuscript.

\resp \review{}

Additional Comments -

\begin{enumerate}

	\cmnts{a} - {The reviewer considers that closing statements regarding the applicability of the proposed schemes are missing. Since the results are quite similar (when not identical), which formulation is preferable between the centralized schemes? Which one for the distributed solutions?}

	\resp \review{}

	\cmnts{b} - {The last discussion in section IV-C could benefit from restructuring. The information on how to obtain a practical distributed precoder design and to avoid backhaul exchange is too condensed and difficult to understand.}

	\resp \review{}

	\cmnts{c} - {For the simulation results, why not to unify configurations when possible? Having to read a different configuration for each graph is cumbersome and no additional comparisons are possible between figures. E.g. PL uniformly distributed between [0,-6] dB in Fig. 2 and [0,-3] dB in Fig. 3.}

	\resp \review{}

	\cmnts{d} - {In Fig. 1, the description of the system model does not agree with the statement of N = 3 subchannels.}

	\resp \review{}

	\cmnts{e} - {In Fig. 4(b), the performance of Q-WSRME seems to be (in average) worse than Q-WSRM. However, that should not be the case, since Q-WSRME is taking into account the over allocation. Any reason for this?}

	\resp \review{}

	\cmnts{f} - {p 6, col 2, row 49: it should be \eqn{t_{l,k,n}} instead of \eqn{t_{l,n,k}}}

	\resp \review{}

	\cmnts{g} - {p 10, col 1, row 28: is it \eqn{\lambda} a dual variable?}

	\resp \review{}

	\cmnts{h} - {p 10, col 2, row 59: typo wHith}

	\resp \review{}

	\cmnts{i} - {In general, a grammar check is recommended, several mistakes with respect to singular and plural nouns have been observed, e.g. -p 6, col 2, row 56 "... for A fixed receiverS" is not correct.}

	\resp \review{}

\end{enumerate}

\end{enumerate}

### 2015-06-22 Report/convergence_distributed.tex
updated

The convergence of the distributed algorithm in Algorithm \ref{algo-3} follows the same discussion as the one in Appendix \ref{sec-3.5}, if the subproblem in \eqref{eqn-decent-1} converges to the centralized solution. The feasible set of the problem in \eqref{eqn-decent-1} satisfies the Slater's constraint by having a non-empty interior and is also compact. Since the subproblem in \eqref{eqn-decent-1} is convex, the convergence of the primal and the \ac{ADMM} scheme can be guaranteed by using the discussions in \cite{bertsekas1999nonlinear,boyd2011distributed} and \cite[Prop. 4.2]{bertsekas1989parallel}.

Unlike the primal or the \ac{ADMM} methods, the decomposition approach via \ac{KKT} conditions, presented in Section \ref{sec-4.3}, updates all the optimization variables at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient method. Therefore, it is difficult to prove theoretically the convergence of the algorithm to a stationary point of the nonconvex problem in \eqref{eqn-6}.

>>>>

The convergence of the distributed algorithm in Algorithm \ref{algo-3} follows the same discussion as the one in Appendix \ref{sec-3.5}, if the subproblem in \eqref{eqn-decent-1} converges to the centralized solution. The feasible set of the problem in \eqref{eqn-decent-1} satisfies the Slater's constraint by having a non-empty interior and is also compact. Since the subproblem in \eqref{eqn-decent-1} is convex, the convergence of the primal and the \ac{ADMM} scheme can be justified by using the discussions in \cite{bertsekas1999nonlinear,boyd2011distributed} and \cite[Prop. 4.2]{bertsekas1989parallel}.

\review{However, if the distributed algorithm is terminated well before the convergence or iterated only for limited iteration, it is difficult to prove the convergence of the algorithm. Since at each \ac{AO} update for \eqn{\mbf{x}^{(i)}}, which involves two \ac{SCA} updates until convergence with limited distributed iterations at each \ac{SCA} step, the objective is not guaranteed to be monotonically decreasing after the distributed iterations, and therefore the convergence is not guaranteed unless the number of iterations is large enough to achieve monotonically decreasing objective. In this case, it converges to a fixed point which is indeed a stationary point for the original nonconvex problem \cite{zangwill1969nonlinear,meyer1976sufficient}}.

Unlike the primal or the \ac{ADMM} methods, the decomposition approach via \ac{KKT} conditions, presented in Section \ref{sec-4.3}, updates all the optimization variables at once, \textit{i.e}, the \ac{SCA} update of \me{\epsilon^{(i-1)}}, the \ac{AO} update of \me{\mvec{w}{l,k,n}} and the dual variable update of \me{\alpha} using subgradient method. Therefore, it is difficult to theoretically prove the convergence of the algorithm to a stationary point of the nonconvex problem in \eqref{eqn-6}.

### 2015-06-22 Report/decomposition_solutions.tex
ordered algorithm locations
submitted_version
updated

The distributed precoder designs for the proposed \ac{JSFRA} scheme are discussed in this section. The \review{convex} formulation in \eqref{eqn-9} or \eqref{eqn-mse-2} requires a centralized controller to perform the precoder design for all users belonging to the coordinating \acp{BS}. In order to design the precoders independently at each \ac{BS} with the minimal information exchange via backhaul, iterative decentralization methods are addressed. In particular, the \acl{PD} and the \ac{ADMM} based \acl{DD} approaches are considered.

Let us consider the \review{convex subproblem with the fixed receive beamformers \me{\mvec{w}{l,k,n}} presented} in \eqref{eqn-9} based on the Taylor series approximation for the nonconvex constraint. The following discussions are equally valid for the \ac{MSE} based solution outlined in \eqref{eqn-mse-2} as well. Since the objective of \eqref{eqn-9} can be decoupled across each \ac{BS}, the centralized problem can be equivalently written as
\begin{subeqnarray} \label{eqn-decent-1} \allowdisplaybreaks
&\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}}& \quad \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \slabel{eqn-decent-1a} \\
&\text{subject to}& \quad \eqref{eqn-9.1c} - \eqref{eqn-9.1e} \IEEEyessubnumber
\end{subeqnarray}
where \me{\tilde{\mbf{v}}_b} denotes the vector of weighted queue deviation corresponding to users \me{k \in \mc{U}_b}.

To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represents the set \me{\mc{U} \backslash \mc{U}_b}. Following an approach similar to the one presented in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be expressed by grouping the interference from each \ac{BS} in \me{\bar{\mc{B}}_{b_k}} as
\iftoggle{single_column}{
\begin{eqnarray}{rCl}\label{eqn-decent-3}
\beta_{l,k,n} & \geq & \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 \nonumber \\
&\quad& + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; \enoise
\end{eqnarray}}{\allowdisplaybreaks
\begin{multline}\label{eqn-decent-3}
\enoise + \sum_{\substack{j = 1,j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b}  \\
+ \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 \leq \beta_{l,k,n}
\end{multline}}
where \me{\zeta_{l,k,n,b}} is the total interference caused by the transmission of \ac{BS} \me{b} to user \me{k \in \mc{U}_{b_k}} in the spatial stream \me{l} and sub-channel \me{n}. It is given by the following upper bound as
\begin{equation} \label{inter_exp}
\zeta_{l,k,n,b} \geq \sum_{i \in \mc{U}_b} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{j,i,n} |^2 \; \forall b \in \bar{\mc{B}}_{b_k}.
\end{equation}

@@

To decentralize the problem in \eqref{eqn-decent-1}, the \ac{BS} specific vector \me{\mbfa{\zeta}_b} in \eqref{if_vector}, which are relevant for the \ac{BS} \me{b}, can either be fixed or treated as a variable in accordance to the decomposition method. To decouple the precoder design across \acp{BS}, the equivalent downlink channel \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n}, \forall k \in {\mc{U}}} are to be known at each \ac{BS} \me{b} through the precoded uplink pilots from all the users in the system, where the precoders are the \ac{MMSE} receiver \me{\mvec{w}{l,k,n}} evaluated at the user. Similarly, to update the \ac{MMSE} receivers at each user \me{k}, the equivalent channels \me{\mvec{H}{b,k,n} \mvec{m}{l,k^{\prime},n}, \forall k^{\prime} \in {\mc{U}_b}, \forall b \in \mc{B}} need to be known through the user specific precoded downlink pilots precoded with the updated transmit beamformers \me{\mvec{m}{l,k,n}, \forall k \in \mc{B}} evaluated at the \ac{BS} \me{b} by using the equivalent downlink channel that includes the updated \ac{MMSE} receivers of all the users, as in \cite{komulainen2013effective}.

%The subproblems with the \ac{BS} specific interference variables are controlled by a master subproblem, which determines the interference variable \me{\zeta_{l,k,n,b}^{\{b_k\}}} in accordance with the global objective.

>>>>

The distributed precoder designs for the proposed \ac{JSFRA} scheme are discussed in this section. The convex formulation in \eqref{eqn-9} or \eqref{eqn-mse-2} requires a centralized controller to perform the precoder design for all users belonging to the coordinating \acp{BS}. In order to design the precoders independently at each \ac{BS} with the minimal information exchange via backhaul, iterative decentralization methods are addressed. In particular, the \acl{PD} and the \ac{ADMM} based \acl{DD} approaches are considered.

Let us consider the convex subproblem with the fixed receive beamformers \me{\mvec{w}{l,k,n}} presented in \eqref{eqn-9} based on the Taylor series approximation for the nonconvex constraint. The following discussions are equally valid for the \ac{MSE} based solution outlined in \eqref{eqn-mse-2} as well. Since the objective of \eqref{eqn-9} can be decoupled across each \ac{BS}, the centralized problem can be equivalently written as
\begin{subeqnarray} \label{eqn-decent-1} \allowdisplaybreaks
&\underset{\substack{\gamma_{l,k,n},\mvec{m}{l,k,n}, \beta_{l,k,n}}}{\text{minimize}}& \quad \sum_{b \in \mc{B}} \| \tilde{\mbf{v}}_b \|_q \IEEEyessubnumber \slabel{eqn-decent-1a} \\
&\text{subject to}& \quad \eqref{eqn-9.1c} - \eqref{eqn-9.1e} \IEEEyessubnumber
\end{subeqnarray}
where \me{\tilde{\mbf{v}}_b} denotes the vector of weighted queue deviation corresponding to users \me{k \in \mc{U}_b}.

To begin with, let \me{\bar{\mc{B}}_b} denote the set \me{\mc{B} \backslash \{b\}} and \me{\bar{\mc{U}}_b} represents the set \me{\mc{U} \backslash \mc{U}_b}. Following an approach similar to the one presented in \cite{pennanen2011decentralized,tolli2011decentralized}, the coupling constraint \eqref{eqn-9.1c} or \eqref{eqn-mse-1.3} can be expressed by grouping the interference from each \ac{BS} in \me{\bar{\mc{B}}_{b_k}} as
\iftoggle{single_column}{
\begin{equation}\label{eqn-decent-3}
\beta_{l,k,n} \geq \sum_{\substack{j = 1\\j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 + \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b} \; + \; \enoise
\end{equation}}{\allowdisplaybreaks
\begin{multline}\label{eqn-decent-3}
\enoise + \sum_{\substack{j = 1,j \neq l}}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,k,n} |^2 + \sum_{b \in \bar{\mc{B}}_{b_k}} \zeta_{l,k,n,b}  \\
+ \sum_{i \in \mc{U}_{b_k} \backslash \{k\}} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{j,i,n} |^2 \leq \beta_{l,k,n}
\end{multline}}
where \me{\zeta_{l,k,n,b}} is the total interference caused by the transmission of \ac{BS} \me{b} to user \me{k \in \mc{U}_{b_k}} in the spatial stream \me{l} and sub-channel \me{n}. It is given by the following upper bound as
\begin{equation} \label{inter_exp}
\zeta_{l,k,n,b} \geq \sum_{i \in \mc{U}_b} \sum_{j = 1}^L |\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n} \mvec{m}{j,i,n} |^2 \; \forall b \in \bar{\mc{B}}_{b_k}.
\end{equation}

@@

To decentralize the problem in \eqref{eqn-decent-1}, the \ac{BS} specific vector \me{\mbfa{\zeta}_b} in \eqref{if_vector}, which are relevant for the \ac{BS} \me{b}, can either be fixed or treated as a variable in accordance to the decomposition method. To decouple the precoder design across \acp{BS}, the equivalent downlink channel \me{\mvec{w}{l,k,n}^\herm \mvec{H}{b,k,n}, \forall k \in {\mc{U}}} are to be known at each \ac{BS} \me{b} through the precoded uplink pilots from all the users in the system, where the precoders are the \ac{MMSE} receiver \me{\mvec{w}{l,k,n}} evaluated at the user. Similarly, to update the \ac{MMSE} receivers at each user \me{k}, the equivalent channels \me{\mvec{H}{b,k,n} \mvec{m}{l,k^{\prime},n}, \forall k^{\prime} \in {\mc{U}_b}, \forall b \in \mc{B}} need to be known through the user specific precoded downlink pilots precoded with the updated transmit beamformers \me{\mvec{m}{l,k,n}, \forall k \in \mc{B}} evaluated at the \ac{BS} \me{b} by using the equivalent downlink channel that includes the updated \ac{MMSE} receivers of all the users, as in \cite{komulainen2013effective}. %The subproblems with the \ac{BS} specific interference variables are controlled by a master subproblem, which determines the interference variable \me{\zeta_{l,k,n,b}^{\{b_k\}}} in accordance with the global objective.

### 2015-06-22 Report/ieee_journal.tex
final_antti_show_adhithya_all
updated

\documentclass[10pt,journal,twocolumn,letterpaper]{./../Styles/IEEEtran}

\usepackage{amsmath,amssymb}
\usepackage{acronym,etoolbox}
\usepackage{graphicx,epstopdf}
\usepackage[ruled]{algorithm2e}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false,font=footnotesize]{subfig}
\usepackage{subeqnarray,multirow,cite,array,setspace,fixltx2e,lineno,verbatim,mathtools}

@@

\subsection{Reduced Complexity Spatial Resource Allocation (\acs{SRA})} \label{sec-3.4}
\review{\input{sub_channel_wsrm}}

\section{Distributed Solutions} \label{sec-4}

\review{\input{decomposition_solutions}}

@@

\subsection{Queuing Analysis over Multiple Transmission Slots} \label{time-correlated}
\review{\input{time_correlated}}

@@

\clearpage

>>>>

\documentclass[10pt,journal,final,letterpaper]{./../Styles/IEEEtran}

\usepackage{amsmath,amssymb}
\usepackage{acronym,etoolbox}
\usepackage{graphicx,epstopdf}
\usepackage[ruled]{algorithm2e}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false,font=footnotesize]{subfig}
\usepackage{multirow,cite,array,setspace,fixltx2e,lineno,verbatim,mathtools,url,subeqnarray}

@@

\subsection{Reduced Complexity Spatial Resource Allocation (\acs{SRA})} \label{sec-3.4}
{\input{sub_channel_wsrm}

\section{Distributed Solutions} \label{sec-4}
\input{decomposition_solutions}

@@

\subsection{Queuing Analysis over Multiple Transmission Slots} \label{time-correlated}
\input{time_correlated}

@@

### 2015-06-22 Report/introduction.tex
updated

In general, the resource allocation problems such as admission control ones can be formulated by assigning a binary variable for each user to indicate the presence or the absence in a particular resource \cite{admission_control}. \review{Alternatively, linear transmit precoders, which are complex vectors, can be implicitly modeled as decision variables, thereby avoiding the use of binary decision variables. After the decision stage, the non-zero precoders are used to determine the transmission rates of users on a space-frequency resource. A zero transmit precoder indicates the absence of the user on a given resource. In this way, the soft decisions are used in the optimization problem and the hard decisions are made after the algorithm convergences}.

@@

\subsubsection*{Main Contributions}
In this paper, we design precoders jointly over space-frequency resources to reduce the number of backlogged packets waiting at each \acp{BS}. The proposed formulation also limits the allocations beyond the number of backlogged packets without explicit rate constraints. \review{Initially, we propose a centralized \ac{JSFRA} formulation, which is solved by two iterative algorithms based on the combination of \ac{SCA} and \ac{AO} due to the nonconvex nature of the problem. The proposed algorithms solve a sequence of convex problems obtained by fixing a subset of optimization variables or by approximating the nonconvex constraints by the convex ones. The first approach is performed by directly relaxing the \ac{SINR} expression, while in the second method, the equivalence between the \ac{MSE} and the \ac{SINR} is exploited.} We then discuss the distributed implementation of the \ac{JSFRA} methods using primal decomposition and the \ac{ADMM}. Finally, we also propose a more practical iterative precoder design by directly solving the \ac{KKT} system of equations for the \ac{MSE} reformulation that is numerically shown to require minimal information exchange for each update. \review{Note that the joint space-frequency channel matrix can be formed by stacking the channel of each sub-channel in a block-diagonal form for all users}.

>>>>

In general, the resource allocation problems such as admission control ones can be formulated by assigning a binary variable for each user to indicate the presence or the absence in a particular resource \cite{admission_control}. Alternatively, linear transmit precoders, which are complex vectors, can be implicitly modeled as decision variables, thereby avoiding the use of binary decision variables. After the decision stage, the non-zero precoders are used to determine the transmission rates of users on a space-frequency resource. A zero transmit precoder indicates the absence of the user on a given resource. In this way, the soft decisions are used in the optimization problem and the hard decisions are made after the algorithm convergences.

@@

\subsubsection*{Main Contributions}
In this paper, we design precoders jointly over space-frequency resources to reduce the number of backlogged packets waiting at each \acp{BS}. The proposed formulation also limits the allocations beyond the number of backlogged packets without explicit rate constraints. Initially, we propose a centralized \ac{JSFRA} formulation, which is solved by two iterative algorithms based on the combination of \ac{SCA} and \ac{AO} due to the nonconvex nature of the problem. The proposed algorithms solve a sequence of convex problems obtained by fixing a subset of optimization variables or by approximating the nonconvex constraints by the convex ones. The first approach is performed by directly relaxing the \ac{SINR} expression, while in the second method, the equivalence between the \ac{MSE} and the \ac{SINR} is exploited. We then discuss the distributed implementation of the \ac{JSFRA} methods using primal decomposition and the \ac{ADMM}. Finally, we also propose a more practical iterative precoder design by directly solving the \ac{KKT} system of equations for the \ac{MSE} reformulation that is numerically shown to require minimal information exchange for each update. Note that the joint space-frequency channel matrix can be formed by stacking the channel of each sub-channel in a block-diagonal form for all users.
